Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Results section summary

@@

\subsection{Building matching statistics}

>>>>

Here we present the results of the statistics collections that were made as part of this project.
First the results of the collision study is presented as how many of the road features of each type display collision with some other feature.
Then the results of the geodata precision is presented.
We will present our estimate of the positional accuracy of the OSM dataset, as well as the dataset completeness and statistics about building correspondence and shape accuracy.

@@

\subsection{Building correspondence statistics}
